---
title: "tumor"
output: html_document
---

## some analysis code related to tumors in liver dataset


```{r}
#library(GSVA)
df_normed_counts = read.csv('../../Liver_share_jason/data/livcan_counts_y4_x69.csv')
df_meta = read.csv('../../../arturito_local/final_R_part/liver/data/livcan_meta_y4_x69_withClusters_0327.csv')

# subset
df_meta_tumor = subset(df_meta, df_meta$snapres1 %in% c(0,4,7,8,9,12,14,16,17,23,24))
df_normed_counts_tumor = subset(df_normed_counts, df_meta$snapres1 %in% c(0,4,7,8,9,12,14,16,17,23,24))
df_meta_tumor$tumor_stat = 'Other'
df_meta_tumor$tumor_stat[df_meta_tumor$snapres1 %in% c(7,8,17)] = 'Core'
```

######### then we run cNMF in the python code


## load the cNMF results into R
```{r}
usage_gep = read.csv('../data/tumor_cnmf25_usage_0327.csv')
usage_gep$X = NULL
topgene_gep = read.csv('../data/top100g_tumor_cnmf25_0327.csv')
print(c(dim(usage_gep),
dim(df_meta_tumor))) # make sure not missing cells
```

## do quick wilcox test and see if diff between groups:

```{r}
# first job compare cnmf difference between core and other tumor
cnmfnum = 25
plist = c()
#wlist = c()

for (i in c(1:cnmfnum)){
  x = subset(usage_gep, df_meta_tumor$tumor_stat == 'Core')[,i]
  y = subset(usage_gep, df_meta_tumor$tumor_stat == 'Other')[,i]
  result = wilcox.test(x, y)
  plist = c(plist, result$p.value)
  #wlist = c(wlist, result$statistic)
}
plist = unlist(plist)
#wlist = unlist(wlist)
padj = p.adjust(plist)
padj
```

#### Plot out all GEPs between groups

```{r}
library(ggpubr)
library(patchwork)

df_meta_tumor$tumor_stat = 'Other'
df_meta_tumor$tumor_stat[df_meta_tumor$snapres1 %in% c(7,8,17)] = 'Infiltrated'
df_meta_tumor$tumor_stat = factor(df_meta_tumor$tumor_stat, levels = c('Other', 'Infiltrated'))

for (i in c(1:25)){
  tempdf = df_meta_tumor
  tempdf$gep = usage_gep[,i]
  tempdf$gep[tempdf$gep > quantile(tempdf$gep, 0.98)] =  quantile(tempdf$gep, 0.98) # 98% quantile
  p = ggplot(tempdf, aes(x=tumor_stat, y=gep, fill = tumor_stat)) + 
    geom_violin(trim=FALSE, width=1)+
    geom_boxplot(width=0.05, fill = 'white', outlier.shape = NA)+
    theme_classic() + ggtitle(paste0('GEP',as.character(i))) +
    scale_fill_manual(values=c("#FFC8C8", "#FC6736")) +
    stat_compare_means(size = 2) + theme(legend.position="none", axis.title.x=element_blank()) +
    ylab("GEP usage")
  #ggsave('../plots/natimm_mac_M1_Features.png', height = 6, width = 7.2)
  assign(paste0('p_',as.character(i)), p)
}
pp = wrap_plots(list(p_1, p_2, p_3, p_4, p_5,
                p_6, p_7, p_8, p_9, p_10, p_11, p_12, p_13, p_14,
                p_15, p_16, p_17, p_18, p_19, p_20,
                p_21, p_22, p_23, p_24, p_25), ncol = 5)
ggsave('../plots/gep_25_compare_0327.png', pp, height = 10, width = 10)
ggsave('../plots/gep_25_compare_0327.svg', pp, height = 10, width = 10)
pp
```

##### all look very different, could consider annotation of the geps


## use enrichR to annotate GEPs
```{r}
library(enrichR)

# test gep top
dbs <- c("GO_Molecular_Function_2015", "GO_Cellular_Component_2015", "GO_Biological_Process_2015")
enriched <- enrichr(topgene_gep$X2[c(1:20)], dbs)
results = enriched$GO_Biological_Process_2015

```

#### violin plot for main fig

```{r}
tl = c(2,19,22,1,3,6) # selected GEPs to show in main fig

for (i in tl){
  tempdf = df_meta_tumor
  tempdf$gep = usage_gep[,i]
  tempdf$gep[tempdf$gep > quantile(tempdf$gep, 0.98)] =  quantile(tempdf$gep, 0.98) # 98% quantile
  p = ggplot(tempdf, aes(x=tumor_stat, y=gep, fill = tumor_stat)) + 
    geom_violin(trim=FALSE, width=1)+
    geom_boxplot(width=0.05, fill = 'white', outlier.shape = NA)+
    theme_classic() + ggtitle(paste0('GEP',as.character(i))) +
    scale_fill_manual(values=c("#FFC8C8", "#FC6736")) +
    stat_compare_means(size = 2) + theme(legend.position="none", axis.title.x=element_blank()) +
    ylab("GEP usage")
  #ggsave('../plots/natimm_mac_M1_Features.png', height = 6, width = 7.2)
  assign(paste0('p_',as.character(i)), p)
}

pp = wrap_plots(list(p_2, p_19, p_22, 
                     p_1, p_3, p_6), ncol = 3)
ggsave('../plots/gep_diff_compare_0327.png', pp, height = 4, width = 6)
ggsave('../plots/gep_diff_compare_0327.svg', pp, height = 4, width = 6)
pp
```

#### then plot tumor subsets locations for supp


## tumor clusters from cellsnap

```{r}
df = df_meta_tumor # df with all the meta labels
plotdf = data.frame(snap_clust = df$snapres1,
                    f_clust = df$featres1,
                    x = df$x_slide_mm,
                    y = df$y_slide_mm
                    )
group.colors <- c( "clust" = "#FF1E00", "None" = "#FFFFFF00")

snap_b = c(0,4,7,8,9,12,14,16,17,23,24)
i = 0
for(clust in snap_b){ # do this by cluster number
  i = i + 1
  print(clust)
  temp = plotdf
  temp$plot = "None"
  temp$plot[temp$snap_clust == clust] = "clust"
  
  p = ggplot(temp, aes(x = x, y = y, color = plot)) +
    geom_point(size = 0.25, stroke = 0.25) + theme_classic() +
    theme(axis.line=element_blank(),
      axis.text.x=element_blank(),
      axis.text.y=element_blank(),
      axis.ticks=element_blank(),
      axis.title.x=element_blank(),
      axis.title.y=element_blank(),
      legend.position="none",
      panel.background=element_blank(),
      panel.border=element_blank(),
      panel.grid.major=element_blank(),
      panel.grid.minor=element_blank(),
      plot.background=element_blank(),
      plot.margin = unit(c(0.0001,0.0001,0.0001,0.0001), "mm")) +
    scale_color_manual(values=group.colors)
  
  assign(paste0("p", i), p)
}

library(patchwork)
pp = wrap_plots(p1,p2,p3,p4,p5,p6,p7,p8,p9,p10,p11, ncol = 4)
pp
ggsave("../plots/snap_tumors_0327.png", height = 6, width = 8)
```


## tumor cluster from feature clustering

```{r}
group.colors <- c( "clust" = "#FF1E00", "None" = "#FFFFFF00")
feat_b = c(0,1,6,7,11)
i = 0
for(clust in feat_b){ # do this by cluster number
  i = i + 1
  print(clust)
  temp = plotdf
  temp$plot = "None"
  temp$plot[temp$f_clust == clust] = "clust"
  
  p = ggplot(temp, aes(x = x, y = y, color = plot)) +
    geom_point(size = 0.25, stroke = 0.25) + theme_classic() +
    theme(axis.line=element_blank(),
      axis.text.x=element_blank(),
      axis.text.y=element_blank(),
      axis.ticks=element_blank(),
      axis.title.x=element_blank(),
      axis.title.y=element_blank(),
      legend.position="none",
      panel.background=element_blank(),
      panel.border=element_blank(),
      panel.grid.major=element_blank(),
      panel.grid.minor=element_blank(),
      plot.background=element_blank(),
      plot.margin = unit(c(0.0001,0.0001,0.0001,0.0001), "mm")) +
    scale_color_manual(values=group.colors)
  
  assign(paste0("p", i), p)
}

library(patchwork)
pp = wrap_plots(p1,p2,p3,p4,p5, ncol = 4)
pp
ggsave("../plots/feat_tumors_0327.png", height = 4, width = 8)
```

#### then we do heatmap, based on gep and top 20 genes:

```{r}
gep_spec = read.csv('../data/gep_spectra_cnmf25_0327.csv', row.names = 1)
top20genes = c()
for (i in c(1:25)){
  gg = topgene_gep[c(1:10),i] # top 20 genes # changed to top10 other wise hard to viz
  top20genes = c(gg, top20genes)
}
top20genes = unique(unlist(top20genes))
#top20genes

gep_spec_sub = gep_spec[top20genes,]
gep_spec_sub = t(scale(t(gep_spec_sub)))
library(pheatmap)
pdf(file="../plots/gene_spectra_top10_0327.pdf",height = 15, width = 5)
pheatmap(gep_spec_sub, cluster_rows=FALSE, cluster_cols=FALSE, fontsize_row = 6,
         color=colorRampPalette(c("#FF00FF", "#000000", "#FFFF00"))(50))
dev.off()
```


