---
title: "liver_plot"
output: html_document
---

########### here we then produce the line plots for metrics

```{r}
metrics = read.csv("../data/CH_result_liv_0325.csv") # metrics prev calced
colorv = c("#f6511d","#ffb400","#00a6ed","#7fb800","#A149FA")
names(colorv) = c('ch_snap', 'ch_feature', 'ch_concact', 'ch_muse', 'ch_spice')
# CH

p = ggplot(metrics,aes(x=k,y=value, colour=variable,fill = variable)) +
  stat_summary(geom = "line", fun.y = mean, size = 0.6) +
  stat_summary(geom = "ribbon", fun.data = mean_cl_normal, fun.args=list(conf.int=0.95), alpha = 0.3, colour = NA) +
  theme_classic()+ ggtitle("spleen CH") + scale_fill_manual(values = colorv) + scale_color_manual(values = colorv)
ggsave("../plots/liv_ch_0325.svg", height = 3, width = 5)
p
```


```{r}
metrics = read.csv("../data/SS_result_liv_0325.csv") # metrics prev calced
colorv = c("#f6511d","#ffb400","#00a6ed","#7fb800","#A149FA")
names(colorv) = c('ch_snap', 'ch_feature', 'ch_concact', 'ch_muse', 'ch_spice')
# CH

p = ggplot(metrics,aes(x=k,y=value, colour=variable,fill = variable)) +
  stat_summary(geom = "line", fun.y = mean, size = 0.6) +
  stat_summary(geom = "ribbon", fun.data = mean_cl_normal, fun.args=list(conf.int=0.95), alpha = 0.3, colour = NA) +
  theme_classic()+ ggtitle("spleen SS") + scale_fill_manual(values = colorv) + scale_color_manual(values = colorv)
ggsave("../plots/liv_ss_0325.svg", height = 3, width = 5)
p
```


```{r}
metrics = read.csv("../data/DB_result_liv_0325.csv") # metrics prev calced
colorv = c("#f6511d","#ffb400","#00a6ed","#7fb800","#A149FA")
names(colorv) = c('ch_snap', 'ch_feature', 'ch_concact', 'ch_muse', 'ch_spice')
# CH

p = ggplot(metrics,aes(x=k,y=value, colour=variable,fill = variable)) +
  stat_summary(geom = "line", fun.y = mean, size = 0.6) +
  stat_summary(geom = "ribbon", fun.data = mean_cl_normal, fun.args=list(conf.int=0.95), alpha = 0.3, colour = NA) +
  theme_classic()+ ggtitle("spleen DB") + scale_fill_manual(values = colorv) + scale_color_manual(values = colorv)
ggsave("../plots/liv_db_0325.svg", height = 3, width = 5)
p
```


```{r}
metrics = read.csv("../data/Mod_result_liv_0325.csv") # metrics prev calced
colorv = c("#f6511d","#ffb400","#00a6ed","#7fb800","#A149FA")
names(colorv) = c('ch_snap', 'ch_feature', 'ch_concact', 'ch_muse', 'ch_spice')
# CH

p = ggplot(metrics,aes(x=res, y=value, colour=variable,fill = variable)) +
  stat_summary(geom = "line", fun.y = mean, size = 0.6) +
  stat_summary(geom = "ribbon", fun.data = mean_cl_normal, fun.args=list(conf.int=0.95), alpha = 0.3, colour = NA) +
  theme_classic()+ ggtitle("spleen Mod") + scale_fill_manual(values = colorv) + scale_color_manual(values = colorv)
ggsave("../plots/liv_mod_0325.svg", height = 3, width = 5)
p
```


######### cell type location plotting

```{r}
df_meta = read.csv('../data/livcan_meta_y4_x69_withClusters_0327.csv')

ggc = c("grey57","#D20062", "#FB8072", "#A6CEE3",
                                "#1F78B4", "#B2DF8A", "#33A02C",
                                "#FFAF45")
names(ggc) = c('Tumor',
    'T',
    'Stellate',
    'Other',
    'Macrophage',
    'LSEC',
    'Hepatocytes',
    'B')

p = ggplot(df_meta, aes(x = x_slide_mm, y = y_slide_mm, color = snapres1_ann, size = 20)) +
    geom_point(size = 0.25, stroke = 0.25) + theme_classic() +
    theme(axis.line=element_blank(),
      axis.text.x=element_blank(),
      axis.text.y=element_blank(),
      axis.ticks=element_blank(),
      axis.title.x=element_blank(),
      axis.title.y=element_blank(),
      #legend.position="none",
      panel.background=element_blank(),
      panel.border=element_blank(),
      panel.grid.major=element_blank(),
      panel.grid.minor=element_blank(),
      plot.background=element_blank(),
      plot.margin = unit(c(0.0001,0.0001,0.0001,0.0001), "mm")) +
      scale_color_manual(values = ggc) + 
    theme(
      plot.background = element_rect(fill = "black")
      )
ggsave("../plots/cell_loc_liver_0327.png",p ,height = 5, width = 6.5)
p
```


#### only do snap macropahge subsets locations

```{r}
df_meta_sub = subset(df_meta, df_meta$snapres1 %in% c(5) | df_meta$snapres1_ann == 'Tumor')
df_meta_sub$temp = 'Other'
df_meta_sub$temp[df_meta_sub$snapres1_ann == 'Tumor'] = 'Tumor'
df_meta_sub$temp[df_meta_sub$snapres1 == 5] = 'target'

ggc = c("grey57","black", "#5FBDFF")
names(ggc) = c('Tumor',
    'Other',
    'target')

df_meta_sub$size = 1
df_meta_sub$size[df_meta_sub$temp == 'target'] = 2

p = ggplot(df_meta_sub, aes(x = x_slide_mm, y = y_slide_mm, color = temp)) +
    geom_point(aes(size = size), stroke = 0.1) + theme_classic() +
    theme(axis.line=element_blank(),
      axis.text.x=element_blank(),
      axis.text.y=element_blank(),
      axis.ticks=element_blank(),
      axis.title.x=element_blank(),
      axis.title.y=element_blank(),
      legend.position="none",
      panel.background=element_blank(),
      panel.border=element_blank(),
      panel.grid.major=element_blank(),
      panel.grid.minor=element_blank(),
      plot.background=element_blank(),
      plot.margin = unit(c(0.0001,0.0001,0.0001,0.0001), "mm")) +
      scale_color_manual(values = ggc) + 
    theme(
      plot.background = element_rect(fill = "black")
      ) +
  scale_size(range = c(0.2, 0.4)) #+ scale_stroke(range = c(0.1, 0.2))
ggsave("../plots/cell_loc_liver_target5_0327.png",p ,height = 3.5, width = 4)
p
```



```{r}
df_meta_sub = subset(df_meta, df_meta$snapres1 %in% c(6) | df_meta$snapres1_ann == 'Tumor')
df_meta_sub$temp = 'Other'
df_meta_sub$temp[df_meta_sub$snapres1_ann == 'Tumor'] = 'Tumor'
df_meta_sub$temp[df_meta_sub$snapres1 == 6] = 'target'

ggc = c("grey57","black", "#DCE319FF")
names(ggc) = c('Tumor',
    'Other',
    'target')

df_meta_sub$size = 1
df_meta_sub$size[df_meta_sub$temp == 'target'] = 2

p = ggplot(df_meta_sub, aes(x = x_slide_mm, y = y_slide_mm, color = temp)) +
    geom_point(aes(size = size), stroke = 0.1) + theme_classic() +
    theme(axis.line=element_blank(),
      axis.text.x=element_blank(),
      axis.text.y=element_blank(),
      axis.ticks=element_blank(),
      axis.title.x=element_blank(),
      axis.title.y=element_blank(),
      legend.position="none",
      panel.background=element_blank(),
      panel.border=element_blank(),
      panel.grid.major=element_blank(),
      panel.grid.minor=element_blank(),
      plot.background=element_blank(),
      plot.margin = unit(c(0.0001,0.0001,0.0001,0.0001), "mm")) +
      scale_color_manual(values = ggc) + 
    theme(
      plot.background = element_rect(fill = "black")
      ) +
  scale_size(range = c(0.2, 0.4)) #+ scale_stroke(range = c(0.1, 0.2))
ggsave("../plots/cell_loc_liver_target6_0327.png",p ,height = 3.5, width = 4)
p
```


```{r}
df_meta_sub = subset(df_meta, df_meta$snapres1 %in% c(10) | df_meta$snapres1_ann == 'Tumor')
df_meta_sub$temp = 'Other'
df_meta_sub$temp[df_meta_sub$snapres1_ann == 'Tumor'] = 'Tumor'
df_meta_sub$temp[df_meta_sub$snapres1 == 10] = 'target'

ggc = c("grey57","black", "#5FBDFF")
names(ggc) = c('Tumor',
    'Other',
    'target')

df_meta_sub$size = 1
df_meta_sub$size[df_meta_sub$temp == 'target'] = 2

p = ggplot(df_meta_sub, aes(x = x_slide_mm, y = y_slide_mm, color = temp)) +
    geom_point(aes(size = size), stroke = 0.1) + theme_classic() +
    theme(axis.line=element_blank(),
      axis.text.x=element_blank(),
      axis.text.y=element_blank(),
      axis.ticks=element_blank(),
      axis.title.x=element_blank(),
      axis.title.y=element_blank(),
      legend.position="none",
      panel.background=element_blank(),
      panel.border=element_blank(),
      panel.grid.major=element_blank(),
      panel.grid.minor=element_blank(),
      plot.background=element_blank(),
      plot.margin = unit(c(0.0001,0.0001,0.0001,0.0001), "mm")) +
      scale_color_manual(values = ggc) + 
    theme(
      plot.background = element_rect(fill = "black")
      ) +
  scale_size(range = c(0.2, 0.4)) #+ scale_stroke(range = c(0.1, 0.2))
ggsave("../plots/cell_loc_liver_target10_0327.png",p ,height = 3.5, width = 4)
p
```


#### umap plotting:

```{r}
ssnap = read.csv('../data/double_snap_combo_stable_0327.csv')
ssnap$X = NULL # first row is rnum
colnames(ssnap) = paste0('PC_', rep(1:ncol(ssnap)))
rownames(ssnap) = paste0('cell_', rep(1:nrow(ssnap)))

library(Seurat)
snp <- CreateSeuratObject(counts = t(ssnap), assay = "cnp")
SetAssayData(object = snp, slot = "data", new.data =t(ssnap), assay="cnp")
snp <- ScaleData(snp) 
snp<- RunPCA(snp, features = rownames(snp))
snp <-  FindNeighbors(snp, dims = 1:30)

# umap plotting
snp <- RunUMAP(snp, dims = 1:30, seed.use = 1)
```


```{r}
library(Polychrome)
set.seed(42)
P26 = createPalette(26,  c("#010101", "#ff0000"), M=1000)
swatch(P26)
```


```{r}
df_meta = read.csv('../data/livcan_meta_y4_x69_withClusters_0327.csv')
embd = data.frame(umap1 = snp@reductions$umap@cell.embeddings[,1],
                  umap2 = snp@reductions$umap@cell.embeddings[,2],
                  label = as.character(df_meta$snapres1))


bkc = P26
names(bkc) = c('0', '1', '2', '3', '4', '5', '6', '7', '8', '9', '10', '11',
               '12', '14', '13', '15', '16', '17', '18', '19','20','21','22',
               '23','24','25')

library(ggplot2)
p1 = ggplot(embd)  + 
  geom_point(aes(x=umap1, y=umap2, color=label,size = 0.2, stroke = 0), cex = 0.7) +
  labs( x = "tsne 1", y = "tsne 2") + theme_classic() + ggtitle("sr") +
  scale_color_manual(values = bkc)
ggsave("../plots/umap_liver_snap_0327.png",p1, height = 7, width = 7.8)
p1
```

### umap from feature

```{r}
feat = read.csv('../data/livcan_counts_y4_x69.csv') # input is normalized gene counts
rownames(feat) = paste0('cell_', rep(1:nrow(feat)))

library(Seurat)
featt <- CreateSeuratObject(counts = t(feat), assay = "cnp")
SetAssayData(object = featt, slot = "data", new.data =t(feat), assay="cnp")
featt <- ScaleData(featt) 
featt<- RunPCA(featt, features = rownames(featt))
featt <-  FindNeighbors(featt, dims = 1:30)

# umap plotting
featt <- RunUMAP(featt, dims = 1:30)
```

```{r}
embd = data.frame(umap1 = featt@reductions$umap@cell.embeddings[,1],
                  umap2 = featt@reductions$umap@cell.embeddings[,2],
                  label = as.character(df_meta$featres1))

library(ggplot2)
p1 = ggplot(embd)  + 
  geom_point(aes(x=umap1, y=umap2, color=label,size = 0.2, stroke = 0), cex = 0.7) +
  labs( x = "tsne 1", y = "tsne 2") + theme_classic() + ggtitle("sr") +
  scale_color_manual(values = bkc)
ggsave("../plots/umap_liver_feat_0327.png",p1,height = 6, width = 7.8)
p1
```


########### then make heatmap seurat flavor, used in supp

```{r}
Idents(featt) = df_meta$snapres1
snap_markers <- FindAllMarkers(featt, only.pos = TRUE)

#snap_markers %>%
#    group_by(cluster) %>%
#    dplyr::filter(avg_logFC > 1) %>%
#    slice_head(n = 20) %>%
#    ungroup() -> top20

levels(Idents(featt)) = c('0', '1', '2', '3', '4', '5', '6', '7', '8', '9', '10', '11',
               '12', '14', '13', '15', '16', '17', '18', '19','20','21','22',
               '23','24','25')
maxcells  <- min(table(Idents(featt)))
#pp = DoHeatmap(subset(featt, downsample = maxcells), features = top20$gene) + NoLegend()
#ggsave('../plots/top20_snapclust_heatmap_test2.pdf', height = 10, width = 10)
```


```{r}
library(dplyr)
snap_markers %>%
    group_by(cluster) %>%
    dplyr::filter(avg_log2FC > 1) %>%
    slice_head(n = 10) %>%
    ungroup() -> top10

pp = DoHeatmap(subset(featt, downsample = maxcells), features = top10$gene, group.bar = FALSE) +
  NoLegend() + 
    theme(text = element_text(size = 8))
ggsave('../plots/top10_snapclust_heatmap_0327.pdf', height = 13, width = 6.5)
ggsave('../plots/top10_snapclust_heatmap_0327.png', height = 13, width = 6.5)
```


########### feature version heatmap


```{r}
Idents(featt) = df_meta$featres1
levels(Idents(featt)) = c('0', '1', '2', '3', '4', '5', '6', '7', '8', '9', '10', '11', '12', '13')
feat_markers <- FindAllMarkers(featt, only.pos = TRUE)
```

```{r}
feat_markers %>%
    group_by(cluster) %>%
    dplyr::filter(avg_log2FC > 1) %>%
    slice_head(n = 10) %>%
    ungroup() -> top10

pp = DoHeatmap(subset(featt, downsample = maxcells), features = top10$gene, group.bar = FALSE) +
  NoLegend()
ggsave('../plots/top10_featclust_heatmap_0327.pdf', height = 13, width = 5)
ggsave('../plots/top10_featclust_heatmap_0327.png', height = 13, width = 5)
```


############ feature macrophage location plots:


```{r}
df_meta_sub = subset(df_meta, df_meta$featres1 %in% c(2) | df_meta$snapres1_ann == 'Tumor')
df_meta_sub$temp = 'Other'
df_meta_sub$temp[df_meta_sub$snapres1_ann == 'Tumor'] = 'Tumor'
df_meta_sub$temp[df_meta_sub$featres1 == 2] = 'target'

ggc = c("lightgrey","black", "red")
names(ggc) = c('Tumor',
    'Other',
    'target')

df_meta_sub$size = 1
df_meta_sub$size[df_meta_sub$temp == 'target'] = 2

p = ggplot(df_meta_sub, aes(x = x_slide_mm, y = y_slide_mm, color = temp)) +
    geom_point(aes(size = size), stroke = 0.1) + theme_classic() +
    theme(axis.line=element_blank(),
      axis.text.x=element_blank(),
      axis.text.y=element_blank(),
      axis.ticks=element_blank(),
      axis.title.x=element_blank(),
      axis.title.y=element_blank(),
      legend.position="none",
      panel.background=element_blank(),
      panel.border=element_blank(),
      panel.grid.major=element_blank(),
      panel.grid.minor=element_blank(),
      plot.background=element_blank(),
      plot.margin = unit(c(0.0001,0.0001,0.0001,0.0001), "mm")) +
      scale_color_manual(values = ggc) + 
    theme(
      plot.background = element_rect(fill = "black")
      ) +
  scale_size(range = c(0.2, 0.4)) #+ scale_stroke(range = c(0.1, 0.2))
ggsave("../plots/cell_loc_liver_feat_2_0327.png",p ,height = 3.5, width = 4)
p

```


```{r}
df_meta_sub = subset(df_meta, df_meta$featres1 %in% c(5) | df_meta$snapres1_ann == 'Tumor')
df_meta_sub$temp = 'Other'
df_meta_sub$temp[df_meta_sub$snapres1_ann == 'Tumor'] = 'Tumor'
df_meta_sub$temp[df_meta_sub$featres1 == 5] = 'target'

ggc = c("lightgrey","black", "red")
names(ggc) = c('Tumor',
    'Other',
    'target')

df_meta_sub$size = 1
df_meta_sub$size[df_meta_sub$temp == 'target'] = 2

p = ggplot(df_meta_sub, aes(x = x_slide_mm, y = y_slide_mm, color = temp)) +
    geom_point(aes(size = size), stroke = 0.1) + theme_classic() +
    theme(axis.line=element_blank(),
      axis.text.x=element_blank(),
      axis.text.y=element_blank(),
      axis.ticks=element_blank(),
      axis.title.x=element_blank(),
      axis.title.y=element_blank(),
      legend.position="none",
      panel.background=element_blank(),
      panel.border=element_blank(),
      panel.grid.major=element_blank(),
      panel.grid.minor=element_blank(),
      plot.background=element_blank(),
      plot.margin = unit(c(0.0001,0.0001,0.0001,0.0001), "mm")) +
      scale_color_manual(values = ggc) + 
    theme(
      plot.background = element_rect(fill = "black")
      ) +
  scale_size(range = c(0.2, 0.4)) #+ scale_stroke(range = c(0.1, 0.2))
ggsave("../plots/cell_loc_liver_feat_5_0327.png",p ,height = 3.5, width = 4)
p
```



##### Plotting related to LR (spatialDM running)

```{r}
lr = read.csv('../data/tum_mac_LRpairs_full_0327_k30_perm200.csv')
lr$X = NULL

## count sig values
library(dplyr)
target = colnames(lr)
lr %>%  mutate(sum_sig = rowSums(.[target] <= 0.05)) -> lr2

quantile(lr2$sum_sig, 0.95) # 10
hist(lr2$sum_sig, breaks = 50)

df_meta = read.csv('../data/livcan_meta_y4_x69_withClusters_0327.csv')
df_meta_tumor_mac = subset(df_meta, df_meta$snapres1 %in% c(0,4,7,8,9,12,14,16,17,23,24,5,6,10,25))
df_meta_tumor_mac$temp_ann = 'Tumor'
df_meta_tumor_mac$temp_ann[df_meta_tumor_mac$snapres1 %in% c(5,6,10,25)] = 'Mac'
table(df_meta_tumor_mac$temp_ann)
```



```{r}
### macrophage only??
df_meta_tumor_mac$sum_sig = lr2$sum_sig
df_meta_tumor_mac$sum_sig[df_meta_tumor_mac$sum_sig > 10] = 10 # 95% quantile for macrohpage population
df_meta_mac = subset(df_meta_tumor_mac, df_meta_tumor_mac$temp_ann == 'Mac')
p = ggplot(df_meta_mac, aes(x = x_slide_mm, y = y_slide_mm, color = sum_sig, size = 40)) +
    geom_point(size = 0.25, stroke = 0.25) + theme_classic() +
    theme(axis.line=element_blank(),
      axis.text.x=element_blank(),
      axis.text.y=element_blank(),
      axis.ticks=element_blank(),
      axis.title.x=element_blank(),
      axis.title.y=element_blank(),
      #legend.position="none",
      panel.background=element_blank(),
      panel.border=element_blank(),
      panel.grid.major=element_blank(),
      panel.grid.minor=element_blank(),
      #plot.background=element_blank(),
      plot.background = element_rect(fill = "black"),
      plot.margin = unit(c(0.0001,0.0001,0.0001,0.0001), "mm")) +
  scale_color_gradient(low = "blue4", high = "orangered")
ggsave("../plots/liver_sigLR_test1_maconlyV5_0327.png",p ,height = 5, width = 6)
ggsave("../plots/liver_sigLR_test1_maconlyV5_0327.svg",p ,height = 5, width = 6)
p
```


############ c8 and other macrophage comparison barplot 


```{r}
temp_meta = subset(df_meta, df_meta$snapres1 %in% c(0,4,7,8,9,12,14,16,17,23,24,5,6,10,25))
lr8 = subset(lr, temp_meta$snapres1 == 6)
lrOther = subset(lr, temp_meta$snapres1 == 5 | temp_meta$snapres1 == 10 | temp_meta$snapres1 == 25)
```


##### top differernt pairs?? by subsampling + percentage


```{r}
library(reshape2)
## need permutation
batch = 20
size = 200

## lr c8
container = matrix(nrow = dim(lr8)[2], ncol = batch)
rownames(container) = target
for (i in c(1:batch)){
  indx = sample(dim(lr8)[1], size)
  temp = lr8[indx,]
  temp %>%  summarise(sum_sig = colSums(.[target] <= 0.05)) -> a
  container[,i] = a$sum_sig/size
}

lr8_permutation = melt(container)

## lr others

container = matrix(nrow = dim(lrOther)[2], ncol = batch)
rownames(container) = target
for (i in c(1:batch)){
  indx = sample(dim(lrOther)[1], size)
  temp = lrOther[indx,]
  temp %>%  summarise(sum_sig = colSums(.[target] <= 0.05)) -> a
  container[,i] = a$sum_sig/size
}

lrOther_permutation = melt(container)

#####
lr8_permutation$type = 'snap6'
lrOther_permutation$type = 'Other'
lrall_perm = rbind(lr8_permutation, lrOther_permutation)

targetslist = unique(lrall_perm$Var1)
plist = c()
log2list = c()
for (target in targetslist){
  x = lr8_permutation$value[lr8_permutation$Var1 == target]
  y = lrOther_permutation$value[lrOther_permutation$Var1 == target]
  log2c = log2(mean(x)/mean(y))
  res = wilcox.test(x,y)
  plist = c(plist, res$p.value)
  log2list = c(log2list, log2c)
}
plist = unlist(plist)
log2list = unlist(log2list)
padjlist = p.adjust(plist, method = 'BH')
resdf = data.frame(name = targetslist, pdj = padjlist, log2list)

# identify top candidates and plot
```


```{r}
library(ggridges)
library(patchwork)

# these ar the top 5 pairs:
cl = c('COL6A1_ITGA3_ITGB1', 'COL6A1_ITGA2_ITGB1', 'CCL8_CCR2', 'THBS1_ITGAV_ITGB3', 'ICAM1_ITGAL_ITGB2')
plotdf = rbind(lr8_permutation, lrOther_permutation)
plotdf = subset(plotdf, plotdf$Var1 %in% cl)

c = 0
for (i in cl){
  c = c + 1
  tempdf = subset(plotdf, plotdf$Var1 == i)
  p = ggplot(tempdf) + 
      geom_density_ridges(aes(x=value, y=type, fill = type)) +
      ggtitle(i) + theme_minimal() + theme(legend.position="none",
                                            axis.title.x=element_blank(),
                                            axis.title.y=element_blank()) +
    scale_fill_manual(values=c("#5FBDFF", "#DCE319FF"))

  assign(paste0('p_',as.character(c)), p)
}
pp = wrap_plots(list(p_1, p_2, p_3, p_4, p_5), ncol = 1)
ggsave("../plots/LR_snap_specific_0327.svg", height = 10, width = 6.5)
pp
```



